---
title: "Plots for Chapter 1"
author: "Jacey Brooks"
date: "10/11/2019"
output: word_document
---

```{r setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)

#install.packages("extrafont")
library(extrafont)
#font_import()
#loadfonts(device="win")

sal <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Date_Location_Transect_Visit_Data_Processed.csv", stringsAsFactors = FALSE)

counts <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Just_Count_Data.csv", stringsAsFactors = FALSE)

counts_long <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Just_Count_Data_by_species_long.csv", stringsAsFactors = FALSE)

substrate <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Location_Transect_Stream_Features_processed.csv", stringsAsFactors = FALSE)

width_depth <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Date_Location_Transect_Visit_Data_Physical_Stream_Features_processed.csv", stringsAsFactors = FALSE)

# Reduce life stage/age into one column for each species
spec <- sal %>%
  ungroup() %>%
  dplyr::select(-type, -up_down, -dist, - visit, -total, -observers, -time_min, -air, -pH, -water, -DO, -EC, -TDS) %>%
  group_by(date, stream, transect) %>%
  pivot_longer(cols = c(DFUSL, DFUSA, DOCHL, DOCHA, DMONL, DMONA, EBISL, EBISA, GPORL, GPORA, PRUBL, PRUBA), names_to = "species" ) %>%
  mutate(spec = substr(species, start = 1, stop = 4)) %>%
  select(-species) %>%
  group_by(date, stream, transect, spec) %>%
  summarise_all(sum) %>%
  pivot_wider(names_from = spec, values_from = value)

sallies <- sal %>%
  left_join(spec) %>%
  select(-DFUSA, -DFUSL, -DOCHL, -DOCHA, -DMONL, -DMONA, -EBISL, -EBISA, -GPORL, -GPORA, -PRUBL, -PRUBA) %>%
  mutate(stream_trans = paste0(stream, "_", transect),
         transect_num = as.integer(as.factor(transect)),
         date = mdy(date),
         up_down = ifelse(is.na(up_down), "REF", up_down))

sallies_long <- sallies %>%
  pivot_longer(cols = c(DFUS, DOCH, DMON, EBIS, GPOR, PRUB), names_to = "species") %>%
  mutate(species = ifelse(species == "DFUS", "Northern Dusky", species),
         species = ifelse(species == "DMON", "Seal", species),
         species = ifelse(species == "DOCH", "Allegheny Mountain Dusky", species),
         species = ifelse(species == "EBIS", "Northern Two-lined", species),
         species = ifelse(species == "GPOR", "Northern Spring", species),
         species = ifelse(species == "PRUB", "Northern Red", species))

# means and sd's
type <- sallies %>%
  dplyr::select(stream, type, transect, up_down)

sub <- substrate %>%
  select(-Date, - Visit, - Section, -X) %>%
  group_by(Stream, Transect) %>%
  summarise_all(max, na.rm = TRUE) %>%
  mutate(Bankfull = ifelse(Bankfull == (-Inf), NA, Bankfull),
         S.C = ifelse(S.C == (-Inf), NA, S.C),
         Sand = ifelse(Sand == (-Inf), NA, Sand),
         Gravel = ifelse(Gravel == (-Inf), NA, Gravel),
         Cobble = ifelse(Cobble == (-Inf), NA, Cobble),
         Boulder = ifelse(Boulder == (-Inf), NA, Boulder),
         Debris = ifelse(Debris == (-Inf), NA, Debris),
         perc_s.c = (S.C/25)*100,
         perc_sand = (Sand/25)*100,
         perc_gravel = (Gravel/25)*100,
         perc_cobble = (Cobble/25)*100,
         perc_boulder = (Boulder/25)*100,
         perc_debris = (Debris/25)*100) %>%
  select(-S.C, -Sand, -Gravel, -Cobble, -Boulder, -Debris)
colnames(sub) <- c("stream", "transect", "bankfull", "silt_clay", "sand", "gravel", "cobble", "boulder", "debris")

wd <- width_depth %>%
  select(-Section, -X, - Visit) %>%
  group_by(Date, Stream, Transect) %>%
  summarise_all(mean, na.rm = FALSE) %>%
  ungroup() %>%
  mutate(Date = ymd(Date))
wd <- wd[-1,]
colnames(wd) <- c("date", "stream", "transect", "mean_wetted_width", "mean_depth")

sallies_all <- sallies %>%
  left_join(wd) %>%
  left_join(sub) 

sal_means <- sallies %>%
  group_by(stream, transect) %>%
  dplyr::select(-date, -observers, -visit, -stream_trans, -transect_num, -type, -up_down) %>%
  summarise_all(mean, na.rm = TRUE) %>%
  left_join(type) %>%
  distinct() %>%
  left_join(sub)

# dsal_sds <- sal %>%
#   group_by(stream, type, transect, up_down) %>%
#   dplyr::select(-date, -observers, -visit) %>%
#   summarise_all(sd, na.rm = TRUE)

```

# Overview

## USE THIS ONE (OR THE BAR GRAPH)
This is a general overview of the surveys/counts. I like this one but may change it to a bar graph of total counts because the means for all of them are 0 (or around there).

```{r overview, echo = FALSE, message=FALSE, warning=FALSE}
# Graph of average count per transect by species
ggplot(stack(counts_long), aes(x=ind, y=values)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Species") + ylab("Individuals/Transect")

# ggplot(stack(counts_long), aes(x = ind, y = values)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), fill = "lightblue") + theme_classic()

ggplot(stack(counts_long), aes(x = ind, y = values)) + 
  geom_bar(data = NULL, stat= "identity", fill = "lightblue")  + 
  theme(axis.text.x = element_text(size = 9),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15, margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  ylab("Total Counts") +
  xlab("Species")

```

## USE THIS ONE

```{r species by stream, echo = FALSE, message=FALSE, warning=FALSE}
sallies_long$stream <- factor(sallies_long$stream,levels = c("ALEX", "BEARHILL", "DUNGHILL", "KOCH", "WSHALEN", "BLUELICK", "ELKLICK", "MILL", "POPLICKTRIB"))

ggplot(sallies_long, aes(x = type, y = value)) + geom_boxplot() + xlab("Stream Type") + ylab("Individuals/Transect") + facet_wrap(~species, nrow = 2, ncol = 3)  + theme(text = element_text(family = "Times New Roman", size = 20, color = "black"),axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        strip.text.x = element_text(size = 19)) + scale_x_discrete(labels = c("Reference", "Remediated"))
```



# GLMM Results

## USE THIS ONE
### Statistically significant results

This was the only statistically significant covariate in all of the models that I ran. This pattern is really neat and shows that all of the DMON individuals were found in waters that had a pH of at least ~6.5.
```{r, dmon-pH, echo = FALSE, message=FALSE, warning=FALSE}
# dmon_glmm <- readRDS("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Results/dmon_glmm_results.rds")
# 
# predicted_df <- data.frame(dmon_pred = exp(predict(dmon_glmm, sal_all, re.form = NA)), mean_wetted_width = sallies$mean_wetted_width, cobble = sallies$cobble)
# 
# ggplot(sallies_all, aes(pH, DMON)) + geom_point() + geom_line(aes(x=pH, y=dmon_pred), data = predicted_df) + theme_classic()

ggplot(sallies_all, aes(x = mean_wetted_width + cobble, DMON)) + geom_point() + geom_smooth(data = sallies_all, method = "glm", formula = y ~ x + theme_classic()

ggplot(sallies_all, aes(x = mean_wetted_width , DMON)) + geom_point() + geom_smooth(data = sallies_all, method = "glm", formula = y ~ x)  + theme(text = element_text(family = "Times New Roman", size = 15),axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  xlab("Mean Wetted Width (m)") + ylab("Seal Salamander Counts") + xlim(0,6) + ylim(-1,12)

ggplot(sallies_all, aes(x = cobble , DMON)) + geom_point() + geom_smooth(data = sallies_all, method = "glm", formula = y ~ x)  + theme(text = element_text(family = "Times New Roman", size = 15),axis.text.x = element_text(size = 20),
        axis.text.y = element_text(size = 25),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  xlab("Mean Percent Cobble") + ylab("Seal Salamander Counts") + xlim(0,100) + ylim(-1,12)

```

# Other metrics not included in the GLMMs

```{r, sallies - percent silt/clay, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies_all, aes(x = EC , EBIS)) + geom_point() + geom_smooth(data = sallies_all, method = "glm", formula = y ~ x)  + theme(text = element_text(family = "Times New Roman", size = 20, color = "black"),axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 23, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  xlab("Electrical Conductivity (μS/cm)") + ylab("Northern Two-Lined Salamander Counts") + xlim(0,150) + ylim(-1,12)
```


## USE THIS ONE
```{r, sallies - percent sand, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies_all, aes(x = cobble , GPOR)) + geom_point() + geom_smooth(data = sallies_all, method = "glm", formula = y ~ x)  + theme(text = element_text(family = "Times New Roman", size = 20, color = "black"),axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 23, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + 
  xlab("Mean Percent Cobble") + ylab("Northern Spring Salamander Counts") + xlim(0,100) + ylim(-1,6)
```
 
 

## USE THIS ONE
```{r, sallies - percent cobble, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sal_means, aes(cobble, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Percent Cobble") + ylab("Average Number of Individuals/Transect") + xlim(0,100) + ylim(-1,12)
```

```{r, sallies - bankfull, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sal_means, aes(bankfull, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Bankfull Width (cm)") + ylab("Average Number of Individuals/Transect")
```

# Characterizing the stream

This graph is not working and dissolved oxygen not worth mentioning anyways...
```{r, DO, echo = FALSE, message=FALSE, warning=FALSE}
dox <- sal_means %>%
  select(stream, DO) %>%
  distinct() 
  
ggplot(dox, aes(x= stream, y = DO)) + theme_classic() + xlab("Stream") + ylab("Dissolved Oxygen (ppm)")
```

## USE THIS ONE
Shows that the limestone sand dumps are working to some extent on pH.
```{r, pH, echo = FALSE, message=FALSE, warning=FALSE}
sallies$up_down <- factor(sallies$up_down, levels = c("UP", "DOWN", "REF"))

ggplot(sallies_all, aes(x = type, y = cobble)) + geom_boxplot(fill = "lightblue") + xlab("Stream Type") + ylab("Mean Percent Cobble") +  theme(text = element_text(family = "Times New Roman", size = 20),axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + scale_x_discrete(labels = c("Reference", "Remediated")) + ylim(0,100)
```

## USE THIS ONE
Shows that EC is still not great downstream...
```{r, EC, echo = FALSE, message=FALSE, warning=FALSE}
sallies$up_down <- factor(sallies$up_down, levels = c("UP", "DOWN", "REF"))

ggplot(sallies, aes(x = up_down, y = EC)) + geom_boxplot(fill = "lightblue") + xlab("Section of Stream") + theme(text = element_text(family = "Times New Roman", size = 20),axis.text.x = element_text(size = 20, color = "black"),
        axis.text.y = element_text(size = 20, color = "black"),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) + scale_x_discrete(labels = c("Upstream", "Downstream", "Reference")) + ylab("Electrical Conductivity (μS/cm)")

```


Not really sure about this one?? The graph isn't working anyways... Don't know why...
```{r, silt_clay boxplot, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sal_means, aes(x = reorder(stream, cobble, FUN = median), cobble)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```


# salamander counts vs up_down

## USE THIS ONE
This one is all of the graphs below but in one graph. I like it but may change it to a bar graph with standard deviations...
```{r species counts by stream}
sallies_long$up_down <- factor(sallies_long$up_down, levels = c("UP", "DOWN", "REF"))

ggplot(sallies_long, aes(x = up_down, y = value)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Stream Section") + ylab("Individuals/Transect") + facet_wrap(~species, nrow = 2, ncol = 3)  + theme(text = element_text(family = "Times New Roman", size = 20, color = "black"),axis.text.x = element_text(size = 20, angle = 45, hjust = 1, color = "black"),
        axis.text.y = element_text(size = 20),
        axis.title.x = element_text(size = 25, margin = margin(t = 20, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 25, margin = margin(t = 0, r = 20, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank(),
        strip.text.x = element_text(size = 19)) + scale_x_discrete(labels = c("Upstream", "Downstream", "Reference"))
```

```{r, DFUS, echo = FALSE, message=FALSE, warning=FALSE}
par(mfrow = c(2:3))
ggplot(sallies, aes(x = reorder(up_down, DFUS, FUN = median), DFUS)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```


```{r, DMON, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies, aes(x = reorder(up_down, DMON, FUN = median), DMON)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, DOCH, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies, aes(x = reorder(up_down, DOCH, FUN = median), DOCH)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, EBIS, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies, aes(x = reorder(up_down, EBIS, FUN = median), EBIS)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, GPOR, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies, aes(x = reorder(up_down, GPOR, FUN = median), GPOR)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, PRUB, echo = FALSE, message=FALSE, warning=FALSE}
ggplot(sallies, aes(x = reorder(up_down, PRUB, FUN = median), PRUB)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```


