---
title: "Plots for WV Herp Summit Poster"
author: "Jacey Brooks"
date: "September 30, 2018"
output: pdf_document
---


# Graphs I would like to use 
```{r read in}
library(ggplot2)
library(dplyr)

sal <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Date_Location_Transect_Visit_Data_Processed.csv", stringsAsFactors = FALSE)
counts <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Just_Count_Data.csv", stringsAsFactors = FALSE)

sal_means <- sal %>%
  group_by(stream, transect, up_down, type) %>%
  dplyr::select(-date, -observers, -visit) %>%
  summarise_all(mean, na.rm = TRUE)

sal_sds <- sal %>%
  group_by(stream, type, transect, up_down) %>%
  dplyr::select(-date, -observers, -visit) %>%
  summarise_all(sd, na.rm = TRUE)

#sal <- sal %>%
 # mutate(type = ifelse(Type == "res", up_down, type))

#counts <- counts %>%
 # mutate()

sal_type <- sal %>%
  group_by(type) %>%
  dplyr::select(-date,-observers, -visit) %>%
  summarise_all(avg_count = colMeans(DFUSL,	DFUSA,	DOCHL,	DOCHA,	DMONL,	DMONA,	EBISL,	EBISA,	GPORL,	GPORA,	PRUBL,	PRUBA))
```

```{r counts}
ggplot(data = counts, aes(x=species, y=total)) + 
  geom_bar(data = NULL, stat= "identity", fill = "darkorange2")  + 
  theme(axis.text.x = element_text(size = 9),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 15, margin = margin(t = 10, r = 0, b = 0, l = 0)),
        axis.title.y = element_text(size = 15, margin = margin(t = 0, r = 10, b = 0, l = 0)),
        axis.line = element_line(colour = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        panel.background = element_blank()) +
  ylab("Total Counts") +
  xlab("Species") 
ggplot(data = counts, aes(x=species, y = total)) + geom_boxplot(fill = "lightblue") + theme_classic()
```

# sal_means box or violin GPORL~type
```{r a}
ggplot(sal_means, aes(x = reorder(type, GPORL, FUN = mean), GPORL)) + geom_boxplot(fill = "lightblue") + theme_bw()
ggplot(sal_means, aes(x = reorder(type, GPORL, FUN = mean), GPORL)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), fill = "lightblue") + theme_bw()
```

# sal or sal_means box DMONA~type
```{r b}
ggplot(sal, aes(x = reorder(type, DMONA, FUN = mean), DMONA)) + geom_boxplot(fill = "lightblue") + theme_bw()
ggplot(sal_means, aes(x = reorder(type, DMONA, FUN = mean), DMONA)) + geom_boxplot(fill = "lightblue") + theme_bw()
```

# sal box EBISL~type
```{r c}
ggplot(sal, aes(x = reorder(type, EBISL, FUN = mean), EBISL)) + geom_boxplot(fill = "lightblue") + theme_bw()
```

# sal or sal_means box EBISL~up_down
```{r d}
ggplot(sal, aes(x = reorder(up_down, EBISL, FUN = mean), EBISL)) + geom_boxplot(fill = "lightblue") + theme_bw()
ggplot(sal_means, aes(x = reorder(up_down, EBISL, FUN = mean), EBISL)) + geom_boxplot(fill = "lightblue") + theme_bw()
```

# line graphs looking at avg count ~ distance for each species
# EBISL had a uptick in counts right after the sand dump, while DFUSA and DOCHA had a downtick
# GPORL and DMONA had very little counts and thus no observable relationship other than the fact that counts were lower than the average for ref streams
```{r e}
ggplot(data = filter(sal_means, type != "ref"), aes(dist, EBISL)) + geom_point() + geom_smooth() + geom_hline(aes(yintercept = mean(unlist(sal_means[which(sal_means$type == "ref"), "EBISL"]), na.rm = TRUE)), colour = "red")
ggplot(data = filter(sal_means, type != "ref"), aes(dist, DOCHA)) + geom_point() + geom_smooth() + geom_hline(aes(yintercept = mean(unlist(sal_means[which(sal_means$type == "ref"), "DOCHA"]), na.rm = TRUE)), colour = "red")
ggplot(data = filter(sal_means, type != "ref"), aes(dist, DFUSA)) + geom_point() + geom_smooth() + geom_hline(aes(yintercept = mean(unlist(sal_means[which(sal_means$type == "ref"), "DFUSA"]), na.rm = TRUE)), colour = "red")
```

# violin sal_means water temp~ type
``` {r f}
ggplot(sal_means, aes(x = reorder(type, water, FUN = median), water)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), fill = "lightblue") + theme_bw()
```

# violin sal_means pH~type
```{r g}
ggplot(sal_means, aes(x = reorder(type, pH, FUN = median), pH)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), fill = "lightblue") + theme_bw()
```

# box sal EC~up_down
```{r h}
ggplot(sal, aes(x = reorder(up_down, EC, FUN = median), EC)) + geom_boxplot(fill = "lightblue") + theme_bw()

```



