---
title: "Plots for Chapter 1"
author: "Jacey Brooks"
date: "10/11/2019"
output: pdf_document
---

```{r, setup, include=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
library(lubridate)

sal <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Date_Location_Transect_Visit_Data_Processed.csv", stringsAsFactors = FALSE)

counts <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Just_Count_Data.csv", stringsAsFactors = FALSE)

counts_long <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Just_Count_Data_by_species_long.csv", stringsAsFactors = FALSE)

substrate <- read.csv("C:/Users/Jacey/Documents/FSU/Research/R_code/MD_Stream_salamanders/Data/Location_Transect_Stream_Features_processed.csv", stringsAsFactors = FALSE)

# Reduce life stage/age into one column for each species
spec <- sal %>%
  ungroup() %>%
  dplyr::select(-type, -up_down, -dist, - visit, -total, -observers, -time_min, -air, -pH, -water, -DO, -EC, -TDS) %>%
  group_by(date, stream, transect) %>%
  pivot_longer(cols = c(DFUSL, DFUSA, DOCHL, DOCHA, DMONL, DMONA, EBISL, EBISA, GPORL, GPORA, PRUBL, PRUBA), names_to = "species" ) %>%
  mutate(spec = substr(species, start = 1, stop = 4)) %>%
  select(-species) %>%
  group_by(date, stream, transect, spec) %>%
  summarise_all(sum) %>%
  pivot_wider(names_from = spec, values_from = value)

sallies <- sal %>%
  left_join(spec) %>%
  select(-DFUSA, -DFUSL, -DOCHL, -DOCHA, -DMONL, -DMONA, -EBISL, -EBISA, -GPORL, -GPORA, -PRUBL, -PRUBA) %>%
  mutate(stream_trans = paste0(stream, "_", transect),
         transect_num = as.integer(as.factor(transect)),
         date = mdy(date),
         up_down = ifelse(is.na(up_down), "REF", up_down))

# means and sd's
type <- sallies %>%
  dplyr::select(stream, type, transect, up_down)

sub <- substrate %>%
  select(-Date, - Visit, - Section, -X) %>%
  mutate(perc_s.c = (S.C/25)*100,
         perc_sand = (Sand/25)*100,
         perc_gravel = (Gravel/25)*100,
         perc_cobble = (Cobble/25)*100,
         perc_boulder = (Boulder/25)*100,
         perc_debris = (Debris/25)*100) %>%
  select(-S.C, -Sand, -Gravel, -Cobble, -Boulder, -Debris) %>%
  group_by(Stream, Transect) %>%
  summarise_all(mean, na.rm = FALSE)
colnames(sub) <- c("stream", "transect", "bankfull", "silt_clay", "sand", "gravel", "cobble", "boulder", "debris")

sal_means <- sallies %>%
  group_by(stream, transect) %>%
  dplyr::select(-date, -observers, -visit, -stream_trans, -transect_num, -type, -up_down) %>%
  summarise_all(mean, na.rm = TRUE) %>%
  left_join(type) %>%
  distinct() %>%
  left_join(sub)

# dsal_sds <- sal %>%
#   group_by(stream, type, transect, up_down) %>%
#   dplyr::select(-date, -observers, -visit) %>%
#   summarise_all(sd, na.rm = TRUE)

```

## Overview

This is a general overview of the surveys/counts.

```{r, overview, echo=FALSE}
# Graph of average count per transect by species
ggplot(stack(counts_long), aes(x=ind, y=values)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Species") + ylab("Individuals/Transect")
# ggplot(sal_means, aes(x = reorder(type, GPORL, FUN = mean), GPORL)) + geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), fill = "lightblue") + theme_bw()


```

## GLMM Results

### Statistically significant results

This was the only statistically significant covariate in all of the models that I ran. This pattern is really neat and shows that all of the DMON individuals 

```{r, dmon-pH, include = TRUE, results = "hide"}
ggplot(sallies, aes(pH, DMON)) + geom_point() + geom_smooth(method = "glm")
```

## Other metrics not included in the GLMMs

```{r, sallies - percent silt/clay, include = TRUE, results = "hide"}
ggplot(sal_means, aes(silt_clay, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Percent Silt/Clay") + ylab("Average number of individuals caught per plot")
```



```{r, sallies - percent sand, include = TRUE, results = "hide"}
ggplot(sal_means, aes(sand, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Percent Sand") + ylab("Average number of individuals caught per plot")
```


```{r, sallies - percent cobble, include = TRUE, results = "hide"}
ggplot(sal_means, aes(cobble, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Percent Cobble") + ylab("Average number of individuals caught per plot")
```

```{r, sallies - bankfull, include = TRUE, results = "hide"}
ggplot(sal_means, aes(bankfull, total)) + geom_point() + geom_smooth(method = "lm") + theme_classic() + xlab("Bankfull Width (cm)") + ylab("Average number of individuals caught per plot")
```

## Characterizing the stream

```{r, DO, include = TRUE, results = "hide", include = TRUE, results = "hide"}
dox <- sal_means %>%
  select(stream, DO) %>%
  distinct() 
  
ggplot(dox, aes(x= stream, y = DO)) + theme_classic() + xlab("Stream") + ylab("Dissolved Oxygen (ppm)")
```
Dissolved oxygen not worth mentioning...


```{r, pH, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, pH, FUN = median), pH)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```


```{r, EC, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, EC, FUN = median), EC)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 

```


```{r, DFUS, include = TRUE, results = "hide"}
par(mfrow = c(2:3))
ggplot(sallies, aes(x = reorder(up_down, DFUS, FUN = median), DFUS)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 

```


```{r, DMON, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, DMON, FUN = median), DMON)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, DOCH, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, DOCH, FUN = median), DOCH)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, EBIS, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, DOCH, FUN = median), DOCH)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, GPOR, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, GPOR, FUN = median), GPOR)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```

```{r, PRUB, include = TRUE, results = "hide"}
ggplot(sallies, aes(x = reorder(up_down, PRUB, FUN = median), PRUB)) + geom_boxplot(fill = "lightblue") + theme_classic() + xlab("Section of Stream") 
```


